%-------------------------
% Resume in Latex
% Author : Jake Gutierrez
% Based off of: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
% \input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
% \pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      {\small#3} & {\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      {\small#1} & {\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------
% \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
%   \textbf{\href{http://sourabhbajaj.com/}{\Large Sourabh Bajaj}} & Email : \href{mailto:sourabh@sourabhbajaj.com}{sourabh@sourabhbajaj.com}\\
%   \href{http://sourabhbajaj.com/}{http://www.sourabhbajaj.com} & Mobile : +1-123-456-7890 \\
% \end{tabular*}

\begin{center}
    \textbf{\Huge \scshape Robert Alexander} \\ \vspace{1pt}
    \small 310-483-4191 $|$ \href{mailto:robalexdr@gmail.com}{\underline{robalexdr@gmail.com}} $|$
    \href{https://linkedin.com/in/robalexdr}{\underline{linkedin.com/in/robalexdr}} $|$
    \href{https://github.com/robalexdr}{\underline{github.com/robalexdr}}
\end{center}


%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Independent}{Jan. 2025 -- Present}
      {Software Engineer}{}
      \resumeItemListStart
        \resumeItem{Building Dishcraft, a full-stack recipe platform with cloud-native infrastructure, normalized data modeling, AI-assisted recipe generation, and personalized recommendation pipelines}
        \resumeItem{Building Quandary, an extensible AI learning platform centered on note-based knowledge management, semantic retrieval, active recall, and configurable learning workflows}
      \resumeItemListEnd

    \resumeSubheading
      {Apkudo}{Sep. 2022 -- Nov. 2024}
      {Senior Software Engineer}{}
      \resumeItemListStart
        \resumeItem{Led engineering for a greenfield, IoT-enabled retail device-logistics platform used to track smartphone shipments for a major telecommunications provider}
        \resumeItem{Developed station software, APIs, and operational workflows supporting device intake, processing, and shipment tracking}
        \resumeItem{Partnered with client managers to define requirements and deliver workflow improvements}
      \resumeItemListEnd

    \resumeSubheading
      {Actium Health}{Jul. 2021 -- Jul. 2022}
      {Software Engineer}{Irvine, CA}
      \resumeItemListStart
        \resumeItem{Built batch and streaming medical-data ingestion pipelines using Python, AWS, MySQL, and Kafka}
        \resumeItem{Developed GraphQL APIs and data-access layers with SQLAlchemy}
        \resumeItem{Built frontend components and pages with React and TypeScript, with Jest-based unit testing}
        \resumeItem{Served as scrum master, facilitating sprint planning, standups, retrospectives, and backlog refinement}
      \resumeItemListEnd

  \resumeSubHeadingListEnd


%-----------ADDITIONAL EXPERIENCE-----------
\section{Additional Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Sense Corp \textnormal{--- Technical Consultant}}{Nov. 2020 -- Feb. 2021}
      {Data science and engineering consulting}{Austin, TX}

    \resumeSubheading
      {UCI CS Department \textnormal{--- Graduate Teaching Assistant}}{Sep. 2018 -- June 2020}
      {Taught discrete math, Python, algorithms, and database courses}{Irvine, CA}

    \resumeSubheading
      {AppDynamics \textnormal{--- Data Engineer}}{Jan. 2018 -- Oct. 2018}
      {Built Python ETL pipelines and Snowflake data warehouse workflows}{San Francisco, CA}

    \resumeSubheading
      {PLAYSTUDIOS \textnormal{--- Data Engineer}}{Aug. 2017 -- Dec. 2017}
      {Developed Snowflake data warehouse and Talend data integration pipelines}{Burlingame, CA}

    \resumeSubheading
      {REAL Software Systems \textnormal{--- Database Developer}}{Mar. 2016 -- May 2017}
      {Automated SQL Server operations and data workflows using T-SQL and PowerShell}{Woodland Hills, CA}

  \resumeSubHeadingListEnd


%-----------EDUCATION-----------
\section{Education}
    \resumeSubHeadingListStart
    \resumeSubheading
      {University of California, Irvine}{Irvine, CA}
      {M.S. Computer Science}{Sept. 2018 -- June 2020}
    \resumeSubheading
      {University of California, Los Angeles}{Los Angeles, CA}
      {B.S. Computational Math}{Sept. 2011 -- June 2015}
  \resumeSubHeadingListEnd


%
%-----------PROGRAMMING SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages}{: TypeScript, SQL, Python} \\
     \textbf{Backend \& Data}{: Postgres, Prisma, Fastify, Express, Node.js, Snowflake, SQL Server } \\
     \textbf{Testing}{: Vitest, Node.js Test Runner, pytest, Jest} \\
     \textbf{Developer Tools}{: Git, Docker} \\
     \textbf{Cloud \& DevOps}{: AWS, AWS CDK, ECS, Fargate, ECR, RDS, CloudWatch, Cognito, GitHub Actions} \\
    }}
 \end{itemize}


%-------------------------------------------
\end{document}
